MSDS6372 - Final Project

### 2018-03-30 MSDS6372_Final_Project_BBHOF.Rmd
Includes PCA and PC plot

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# required libraries
library(kableExtra) # to make uber sexy tables for output
library(pastecs) # for easy descriptive statistics

@@

# remove non-numeric features
BBHOF_PCA <- BBHOFRaw[,!(colnames(BBHOFRaw) %in% dropcolumns)]

BHHOF_PCA <- prcomp(BBHOF_PCA, center=TRUE, scale.=TRUE)

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# required libraries
library(kableExtra) # to make uber sexy tables for output
library(pastecs) # for easy descriptive statistics
library(ggbiplot) # implementation of biplot using ggplot2 for plotting PCs

@@

# remove non-numeric features and features with missing values (NEED TO REVISIT THIS)
dropcolumnsPCA <- c("Name", "PrimaryPositionPlayed", "HOFMembership", "Strikeouts", "StolenBases", "CaughtStealing", "StolenBaseRuns")
BBHOF_PCA <- BBHOFRaw[,!(colnames(BBHOFRaw) %in% dropcolumnsPCA)]

# extract labels (player made it into HOF), convert to factor
BBHOF_Labels_PCA <- BBHOFRaw["HOFMembership"]
BBHOF_Labels_PCA$HOFMembership <- as.factor(BBHOF_Labels_PCA$HOFMembership)

# perform PCA
BBHOF_PCA <- prcomp(BBHOF_PCA, center=TRUE, scale.=TRUE)
# since the labels also include 2, converting those to 1, so the result is truly binary (1, 0)
BBHOF_Labels_PCA$HOFMembership[BBHOF_Labels_PCA$HOFMembership == 2] <- 1

# print principal components
print(BBHOF_PCA)

# summary of principal components
summary(BBHOF_PCA)

@@

```{r, echo=TRUE, fig.width=15, fig.height=10}
# plot PCs using ggbiplot
ggbiplot(BBHOF_PCA, obs.scale=1, var.scale=1, groups=BBHOF_Labels_PCA$HOFMembership, ellipse=TRUE, circle=TRUE) + theme(legend.position='top') + scale_color_discrete()
